\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-28 paper/paper.tex
Fix broken refs, address various compilation problems (compiles)

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

@@

The structure of the paper is as follows. In Section~\ref{Motivating example}, we describe, as a motivating example, the Backblaze Hard Drive data set. In Section~\ref{sec:Background}, we introduce our proposed method and potential applications and examine previous related work in the literature. Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of the Backblaze data. In section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. In section~\ref{sec:Data analysis} we illustrate applying the hierarchical GLFP model to a real data set. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Finally, in section~\ref{sec:Conclusions}, we discuss the strengths and limitations of our method and consider extensions and alternatives.

@@

\section{Motivating Example}
\subsection{Backblaze hard drive data}
\label{sec:Data}
Backblaze is a company that offers cloud backup storage to protect against data loss.  Since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods.  Drives are run until failure.  When a hard drive fails it is permanently removed and replaced.  In addition, the number of storage pods is increasing as Backblaze adds drives to its storage capacity.  Every quarter Backblaze makes its data publicly available through their website \citep{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided.  Backblaze does, however, encourage others to further analyze its data.

@@

\begin{figure}
\centering
\includegraphics{dm4-exception}
\caption{\small Top: Event plot for uniform random sample of 60 units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_4,i, \infty)$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{4,i}\mbox{, where }c_{4,i}=0$.\\ Bottom: The adjusted Kaplan-Meier estimate (solid step function) substantially higher than the pointwise posterior median (dashed line; shaded region showing 90\% credible interval) due to several early failures while few were at risk.  Using the same Kaplan-Meier estimator, but only the data truncated after 2500 hours (dotted line) shows close agreement with the posterior median.}

@@

\begin{figure}
{\centering
\includegraphics{dm43-shrinkage}}
\caption{\small Top: Event plot for all units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_{43},i, \infty)$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{43,i}\mbox{, where }c_{43,i}=0$.\\ Bottom: The solid step function correponds to the adjusted Kaplan-Meier estimate. Due to the absence of collected information about early life for this particular model,due to left-truncation, the posterior median (dashed line) follows the ``global model" (dotted line), i.e. the posterior median of proportion failing for a new drive-model, approximately until the beginning of the earliest observational period.}
\label{fig:ex-mod-43}
\end{figure}

@@

\pagebreak
\section{Posterior predictive graphical checks}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-1.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-2}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-3.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-4.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-5.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-6.pdf}
\end{figure}
\clearpage
%\bibliographystyle{plainnat}
\bibliographystyle{asa}
% \bibliographystyle{plain}
\bibliography{sample}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

The structure of the paper is as follows. In Section~\ref{sec:Background}, we introduce our proposed method and potential applications and examine previous related work in the literature. In Section~\ref{sec:Data}, we describe the Backblaze Hard Drive data set, which is used throughout as a motivating example. Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of the Backblaze data. In section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. In section~\ref{sec:Data analysis} we illustrate applying the hierarchical GLFP model to a real data set. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Finally, in section~\ref{sec:Discussion}, we discuss the strengths and limitations of our method and consider extensions and alternatives.

@@

\section{Motivating Example}
\label{sec:Data}
\subsection{Backblaze hard drive data}
Backblaze is a company that offers cloud backup storage to protect against data loss.  Since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods.  Drives are run until failure.  When a hard drive fails it is permanently removed and replaced.  In addition, the number of storage pods is increasing as Backblaze adds drives to its storage capacity.  Every quarter Backblaze makes its data publicly available through their website \citep{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided.  Backblaze does, however, encourage others to further analyze its data.

@@

\begin{figure}
\centering
\includegraphics{dm4-exception}
\caption{\small Top: Event plot for uniform random sample of 60 units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_4,i, \infty)$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{4,i}\mbox{, where }c_{4,i}=0$.\hspace{\textwidth}Bottom: The adjusted Kaplan-Meier estimate (solid step function) substantially higher than the pointwise posterior median (dashed line; shaded region showing 90\% credible interval) due to several early failures while few were at risk.  Using the same Kaplan-Meier estimator, but only the data truncated after 2500 hours (dotted line) shows close agreement with the posterior median.}

@@

\begin{figure}
\centering
\includegraphics{dm43-shrinkage}
\caption{\small Top: Event plot for all units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_{43},i, \infty)$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{43,i}\mbox{, where }c_{43,i}=0$.\hspace{\textwidth}Bottom: The solid step function correponds to the adjusted Kaplan-Meier estimate. Due to the absence of collected information about early life for this particular model,due to left-truncation, the posterior median (dashed line) follows the ``global model" (dotted line), i.e. the posterior median of proportion failing for a new drive-model, approximately until the beginning of the earliest observational period.}
\label{fig:ex-mod-43}
\end{figure}

@@

\pagebreak
\section{Posterior predictive graphical checks}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-1.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-2}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-3.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-4.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-5.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-6.pdf}
\end{figure}
\clearpage
%\bibliographystyle{plainnat}
% \bibliographystyle{plain}
\bibliography{./sample}
